
\noindent We are particularly grateful to the organized efforts of those maintaining the \textcolor{blue}{\href{http://scdb.wustl.edu/}{Supreme Court Database}}, which is principally hosted by Washington University in St.Louis, Missouri.\footnote{Harold J. Spaeth, Lee Epstein, et al. 2022 Supreme Court Database, Version 2022 Release 1. URL: \url{http://Supremecourtdatabase.org}} Their data was pivotal for constructing longitudinal analyses that place the Justices' decision-making during the 2023 term into the broader scope of history. \\

\noindent Apart from data used to develop longitudinal analyses, this report was compiled independently and drew on a multitude of resources to sufficiently track developments and behaviors expressed in the Court's oral arguments, decisions, and docket, among other things. These include, but are not limited to, the Supreme Court's \textcolor{blue}{\href{https://www.supremecourt.gov/}{Official Website}}, \textcolor{blue}{\href{https://www.oyez.org/}{Oyez}}, and \textcolor{blue}{\href{https://www.justia.com/}{Justia}}, among others. \\

\noindent All data used to compile this report will be available \textcolor{blue}{\href{https://empiricalscotus.com/2023-stats/}{HERE}}. There you will find a collection of CSV (.csv) files containing data relevant to the accompanying analyses on \emph{Decisions} and \emph{Oral Arguments} provided in this report. \\

\noindent We are, of course, happy to provide any additional insights and guidance on replication of data and other analysis in this report. For help, please \textcolor{blue}{\href{mailto:adam@feldmannet.com}{Contact Us}}. \\

\noindent We ask that any publication incorporating these data or other material from our report provide a corresponding citation acknowledging the authors, EmpiricalSCOTUS, and any relevant data sourcs indicated with the enclosed tabular information. \\

\noindent Example Citation: Feldman, A. \& Truscott, J. S. (2024, July 1). Supreme Court 2023-2024 Term Stat Review (Version 1.1). \emph{EmpiricalSCOTUS}. Available at: \url{https://empiricalscotus.com/}
